### 2014-03-14 src/analysis.Rnw
update

% \begin{figure*}[t]
% <<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
% ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
% @
% \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
% \label{fig:xsamplesel}
% \end{figure*}
% 
% \begin{figure*}[t]
% <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
% ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
% @
% \caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
% \label{fig:xroundsel}
% \end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
# @
# \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
# \label{fig:xsamplesel}
# \end{figure*}
# 
# \begin{figure*}[t]
# <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")

o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")

o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")

o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

% \begin{figure*}[t]
% <<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
% ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
% @
% \caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
% \label{fig:locsel}
% \end{figure*}
% 
%\begin{figure*}[t]
%<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
%o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
%ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
%  stat_boxplot(geom ='errorbar')+
%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
%@
%\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
%\label{fig:wlocsel}
%\end{figure*}
%
%
%The results of this selection criteria are provided in Table~\ref{tbl:locsel}. The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.

@@

<<one>>=
#3
@
%\begin{figure*}[t]
%<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
%o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
%ggplot(subset(o.one, values < 100 & (type=='line' | type=='method')), aes(power, values, fill=interaction(type,power), dodge=type)) +
%  stat_boxplot(geom ='errorbar')+
%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
%@
%\caption{The effect of one element selection, All are above 0.98 $R^2$.}
%\label{fig:onesel}
%\end{figure*}
%
% ----------------------------------------------------------------------

>>>>

% \begin{figure*}[t]
% <<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
% @
% \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
% \label{fig:xsamplesel}
% \end{figure*}
% 
% \begin{figure*}[t]
% <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
% ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
% @
% \caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
% \label{fig:xroundsel}
% \end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
# @
# \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
# \label{fig:xsamplesel}
# \end{figure*}
# 
# \begin{figure*}[t]
# <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")

o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")

o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")

o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
o.xp.opsel <- colnames(o.xp.opsel)[]
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"

ggplot(subset(o.xp.opsel, reduction < 1000), aes(num.operators, reduction, fill=interaction(type,num.operators), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="opsel(x)")
@
\caption{Operator selection}
\label{fig:xroundsel}
\end{figure*}

% \begin{figure*}[t]
% <<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
% ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
% @
% \caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
% \label{fig:locsel}
% \end{figure*}
% 
%\begin{figure*}[t]
%<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
%o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
%ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%  stat_boxplot(geom ='errorbar')+
%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
%@
%\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
%\label{fig:wlocsel}
%\end{figure*}
%
%
%The results of this selection criteria are provided in Table~\ref{tbl:locsel}. The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.

@@

<<one>>=
#3
@
%\begin{figure*}[t]
%<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
%o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
%ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%  stat_boxplot(geom ='errorbar')+
%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
%@
%\caption{The effect of one element selection, All are above 0.98 $R^2$.}
%\label{fig:onesel}
%\end{figure*}
%
% ----------------------------------------------------------------------

### 2014-03-14 src/methodology.Rnw
update

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

>>>>

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
#o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
#o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(reduction~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(reduction~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
#r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
#r.det$ind <- clean(r.det$ind)
with(r.all,boxplot(reduction~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
with(r.det,boxplot(reduction~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

### 2014-03-14 src/results.Rnw
update

Our results for x\% sampling over program elements are given
in Table~\ref{tbl:xselsample}. The result of its variation, using
\textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result
of using \textit{ceil(sample)} is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  Third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
Fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criteria for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

@@

>>>>

Our results for random sampling over program elements using $sample(x)$
are given in Table~\ref{tbl:xselsample}. The result of its variation, using
$round(x)$ is given in Table~\ref{tbl:xselround}, and that using
$ceil(x)$ is given in Table~\ref{tbl:xselceil}.
The first column in each table provides the scope of sampling i.e. if it was
done per class, per method, per line etc. The second column provides the
fraction involved.  Third column contains the $R^2$ value obtained between
the mutation score of the sampling criteria used and the full mutation score.
The fourth column contains the mutant reduction factor. This is the average of
total mutants produced divided by the number of mutants sampled by the criteria.
Fifth column contains the standard deviation of the same. A few of the projects
did not return any value for certain sampling criteria for particular mutation
reduction fractions. The sixth column contains the number of projects that
actually had valid values for the criteria being considered. The seventh column
is the average multiplier between the sampled mutation score and the full mutation
score.

@@

The same (only for original test suite) is visualized in Figure~\ref{fig:xroundsel}.
